Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-24 paper.tex
Change to paper up to 2D Moss relation

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
In fact, some pioneering work\cite{Moss_1950_relation} discovered
relationships between the dielectric constant $\varepsilon$ and other
physical properties, in particular the band gap $E_{\mathrm{g}}$
(minimal optical transition energy) of bulk
semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
relationship, known as the Moss relation:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Other similar semi-empirical models for the relationship between
$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
been proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
the minor difference between the formulae used, it is clear that there
exists certain general electronic relations in bulk
semiconductors. The existence of such general relationship is also of
high practical importance: it is generally more straightforward and
accurate to measure the band gap $E_{\mathrm{g}}$ than the static
dielectric constant $\varepsilon$, as the latter is strongly dependent
on several critical details on the sample measurements, such as
contamination, disorder, and model interpretation. With the Moss
relationship or other similar models, it is feasible to predict the
dielectric constant of a bulk semiconductor with a reasonable degree
of certainty.

While the relation between the electronic and dielectric properties
for bulk semiconductors are well-established, it is unknown if such
relation still exists in low-dimensional materials. For instance,
two-dimensional (2D) materials, the atomically-thin crystalline layers
\cite{Novoselov_2016}, are known to have distinct electronic
\cite{Mak_2010,Tran_2014} and dielectric properties
\cite{Keldysh_1979_eps_multi,Sharma_1985} compared with their bulk
counterparts, making the empirical relations of dielectric constant in
bulk materials, like the Moss relation invalid within the context of
2D materials. More critically, the static dielectric constant, a
quantity associated with the macroscopic dielectric property and
commonly obtained by theoretical calculations of 2D materials
\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
describe the microscopic and anisotropic dielectric nature of 2D
materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
accurate description of the 2D dielectric nature is the prerequisite
for a 2D Moss-like relation. Here we show that instead of the
dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
correctly captures the dielectric nature of a 2D material for both
in-plane and out-of-plane polarizations. Based on first principles
simulation of over 50 kinds \todo{some more?} of monolayer 2D
materials, we reveal the long-sought universal dielectric scale
relation in the 2D world: the in-plane polarizability
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while the out-of-plane polarizability
$\alpha^{\perp}$ is closely related with the intrinsic thickness of 2D
materials. The anisotropy of the 2D polarizability is further
explained by a confined quantum model. The universal relations provide
quantitative prediction of the dielectric properties of 2D materials,
which leads to better design and understanding of electronic devices
based on 2D materials and their heterostructures. Furthermore, such
relations bridge the dielectric properties between the 2D materials
and their 3D counterparts, and ultimately pushes the boundary of the
understanding of electronic screening in both dimensions.

@@

shown in Figure \ref{fig-1}a \todo{I'll change upon your change of Fig
  1a}, in first principles calculations, an isolated 2D material is
placed in the xy-plane of a periodically repeating superlattice (SL)
with a length $L$ along the z-direction. The macroscopic dielectric
tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, from
fundamental electrostatics, is determined by the response of
volumetric dipole density $\boldsymbol{P}^{p}$, under small perturbative
external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the
directions in $(x, y, z)$, such that:

@@

$\kappa$ is the dielectric tensor of the environment, $\boldsymbol{u}$
is the total dipole moments of the SL, $\rho$ is the spatial charge
density, $\Omega=AL$ is the volume of the SL, $A$ is the xy-plane area
of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the

@@

dielectric tensor ($p \neq q$) tend to be negligible.  Consider that
the 2D material is placed in vacuum, such that $\kappa^{pp} = 1$
and $\kappa^{pq} = 0$, we can distinguish two components of the
SL dielectric tensor, namely the in-plane

@@

$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$
\todo{geometry or numerical average?}. Due to the absence of bonding
along the z-direction, the induced charge density of a 2D material is
highly confined. Figure \ref{fig-1}a demonstrates the charge density
difference between zero and finite electric fields,

@@

$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which only
extends to ~12 \AA{} along the z-direction. When $L$ is
large enough that the induced dipoles from periodic images do not
overlap, the total dipole moments $\boldsymbol{u}$ of the SL in
Eq. \ref{eq:def-eps-2} is independent of $L$. As a consequence, we can
see from Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both

@@

$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on the SL length $L$. We
show this by plotting $\epsilon^{\parallel}_{\mathrm{SL}}$ and
$\epsilon^{\perp}_{\mathrm{SL}}$ as functions of $L$ for 2H-type group
6 transitional metal dichalcogenides (TMDCs, 2H-MX$_{2}$, where M=Mo,
W and X=S, Se, Te), in the top panels of Figure \ref{fig-1}b and
\ref{fig-1}c \todo{change order!}, respectively. We also observe
that neither $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
$\varepsilon^{\perp}_{\mathrm{SL}}$ converges with the superlattice
length $L$ due to fact that the long-range Coulomb interaction could
not be completed screened, which is computationally unpractical

@@

$\varepsilon_{\mathrm{SL}}$ to present the dielectric nature of a 2D

@@

discussed previous, since the total dipole moments $\mathbf{u}$ remain
constant with $L$, we can define the surface or sheet polarization
density matrix $\boldsymbol{\mu}$, by multiplying
Eq. \ref{eq:def-eps-2} with $L$, that

@@

\rho(\boldsymbol{r}) \boldsymbol{r}^{p}d^{3} \boldsymbol{r}/A$,
independent of the superlattice size. Similar to the definition of

@@

We note that the dielectric properties of 2D materials are also often
modeled using an effect medium approach, which treats the 2D material
as a slab with effective permittivity $\varepsilon_{\mathrm{2D}}$ and
thickness $\delta$
\cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
methods require \textit{a priori} determination of $\delta$, a
quantity with controversial definitions \cite{Mas_Ballest__2011}. In
such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
determined by fitting the $L$-dependent data of
$\varepsilon_{\mathrm{SL}}$, which is not only computational
expensive, but also fails to capture the anisotropy of the 2D
dielectric properties (details see Supplementary Section S1). On the
other hand, calculating 2D polarizabilities requires no knowledge of
$\delta$ (see Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
the polarizability as the true descriptor of 2D dielectric properties,
we will reveal the universal Moss-like relation of 2D materials.

@@

We study several types of 2D materials of different electronic and
optical properties, including transition metal dichalcogenides (TMDCs,
with the formula MX\(_{\text{2}}\), where M is a metal in group 4, 6,
10 and X=O, S, Se, Te), metal monochalcogenides (Ga$_{2}$S$_{2}$,
Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl, I), hexagonal boron
nitride (BN), graphene derivatives (fluorographene (C$_{2}$F$_{2}$),
graphane (C$_{2}$H$_{2}$)) and phosphorene (P$_{4}$).  For the TMDCs,
we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2 space
group) and 1T (P3m1 space group).  The structures and elements of the
2D materials are shown in Figure \ref{fig-2}a and \ref{fig-2}b,
respectively. The static 2D polarizabilities are calculated from the
static dielectric response of the selected 2D materials using density
functional theory (DFT) with the Heyd-Scuseria-Ernzerhof hybrid
functionals (HSE06) using the Vienna Ab Initio Simulation Package (VASP)
including spin-orbit coupling to avoid limitations on the description
of band gaps and dielectric functions. Further details for the first
principle calculations please refer to \textit{Methods}.

Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
(blue dots) and polarizabilities (bar plots) of all the 2D materials
investigated, covering a wide bandgap range from far infrared to
ultraviolet. From dimension analysis, it is more intuitive to express
the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which has unit
of \AA. We find that $\alpha^{\parallel}$ has a general descending
trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (more
details see Supplementary Section S2.2).  Combining recent theoretical
findings of the universal linear relation between exciton binding
energy $E_{\mathrm{b}}$ and bandgap $E_{\mathrm{b}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to guess that
a general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha^{\parallel}$ may exist for 2D materials. On the other hand,
the bandgap-independent relation of $\alpha^{\perp}$ resembles
molecular polarizabilities of conjugate molecules \cite{Davies_1952},
fullerenes \cite{Sabirov_2014} and carbon nanotubes
\cite{Benedict_1995}, which are shown to be geometry-dependent. Next
we show that the universal Moss-like relations exist for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$.

@@

xy-planeAccording to the random phase approximation (RPA)

@@

  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\boldsymbol{q}|^{2} \Omega}

>>>>

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
In fact, some pioneering work\cite{Moss_1950_relation} discovered
relations between the dielectric constant $\varepsilon$ and other
physical properties, in particular the band gap $E_{\mathrm{g}}$
(minimal optical transition energy) of bulk
semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
relation, known as the Moss relation:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Other similar semi-empirical models for the relations between
$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
been proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
the minor difference between the formulae used, it is clear that there
exists certain general electronic relations in bulk
semiconductors. The existence of such general relationship is also of
high practical importance: it is generally more straightforward and
accurate to measure the band gap $E_{\mathrm{g}}$ than the static
dielectric constant $\varepsilon$, as the latter is strongly dependent
on several critical details on the sample measurements, such as
contamination, disorder, and model interpretation. With the Moss
relationship or other similar models, it is feasible to predict the
dielectric constant of a bulk semiconductor with a reasonable degree
of certainty.

While the relations between the electronic and dielectric properties
for bulk semiconductors are well-established, it is unknown if such
equation still exists in low-dimensional materials. One important
feature in atomically-thin 2D materials \cite{Novoselov_2016} is that
the electric screening is attenuated and anisotropic
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012}. This
makes the empirical relations of dielectric constants in bulk
materials, like the Moss relation invalid within the context of 2D
materials. More critically, the static dielectric constant, a quantity
associated with the macroscopic dielectric and optoelectronic
properties and commonly obtained by theoretical calculations of 2D
materials \cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may
not well describe this microscopic and anisotropic dielectric nature
of 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
accurate description of the 2D dielectric nature is the prerequisite
for a 2D Moss-like relation, which could be used to make predictions
for less-investigated layered crystals and to create materials design
rules at an accurate level.  Here we show that instead of the
dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
correctly captures the dielectric nature of a 2D material for both
in-plane and out-of-plane polarizations. Based on first principles
simulation using highly accurate hybrid functionals and analytical
models, we reveal the long-sought universal dielectric-scale relation
in the 2D world: the in-plane polarizability $\alpha^{\parallel}$ is
inversely proportional to the minimal bandgap $E_{\mathrm{g}}$, while
the out-of-plane polarizability $\alpha^{\perp}$ is directly related
with the intrinsic thickness of 2D materials. An analytical
quantum-mechanical model is developed which give a sound background to
the dielectric-scale relationships. Furthermore, such relations unify
the dielectric properties between the 2D materials and their 3D
counterparts in a natural manner, which ultimately pushes the boundary
of the understanding of electronic screening in both dimensions. The
discovery of scaling relationships between dielectric and electronic
and structural properties in 2D compounds introduces a new and general
pathway for the exploration of their complex physical and chemical
phenomena well beyond the currently possible applications.

@@

shown in Figure \ref{fig-1}a, in routine first principles
calculations, an isolated 2D material is placed in the xy-plane of a
periodically repeating superlattice (SL) with a length $L$ along the
z-direction separating the cell images. The macroscopic dielectric
tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, is
determined through fundamental electrostatics by the response of the
polarization density $\boldsymbol{P}^{p}$, under small
perturbative external field $\boldsymbol{E}^{q}$, where $p$, $q$ are
the directions in $(x, y, z)$, such that:

@@

where $\kappa$ is the dielectric tensor of the environment,
$\boldsymbol{u}$ is the total dipole moments of the SL, $\rho$ is the
spatial charge density, $\Omega=AL$ is the volume, $A$ is the xy-plane
area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the

@@

dielectric tensor ($p \neq q$) tend to be negligible.  Considering
that the 2D material is placed in vacuum, such that $\kappa^{pp} = 1$
and $\kappa^{pq} = 0$, we can distinguish two components of the SL
dielectric tensor, namely the in-plane

@@

$\varepsilon_{\mathrm{SL}}^{\perp} =
\varepsilon_{\mathrm{SL}}^{zz}$. Due to the absence of bonding along
the z-direction, the induced charge density of a 2D material is highly
confined in the xy-plane but delocalised along of the
z-direction. Figure \ref{fig-1}a shows the charge density difference
between zero and finite electric fields,

@@

$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which extends to
$\sim{}$12 \AA{} along the z-direction. When $L$ is large enough, the
induced dipoles from periodic images do not overlap, and the total
dipole moments $\boldsymbol{u}$ of the SL in Eq. \ref{eq:def-eps-2} is
independent of $L$. As a consequence, we can see from
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both

@@

$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on $L$. We show this by
plotting $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
theory (DFT) as functions of $L$ for P$\bar{6}$m2 (2H) transitional
metal dichalcogenides (TMDCs, 2H-MX$_{2}$, where M=Mo, W and X=S, Se,
Te), in the top panels of Figure \ref{fig-1}b and \ref{fig-1}c,
respectively. We observe that neither
$\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
$\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
that the long-range Coulomb interaction could not be completed
screened within the range of magnitudes computationally accessible

@@

$\varepsilon_{\mathrm{SL}}$ to represent the dielectric nature of a 2D

@@

discussed previously, since the total dipole moments $\mathbf{u}$
remain constant with $L$, we can define the surface or sheet
polarization density matrix $\boldsymbol{\mu}$, by multiplying
Eq. \ref{eq:def-eps-2} with $L$, such that

@@

\rho(\boldsymbol{r}) \boldsymbol{r}^{p}d^{3} \boldsymbol{r}/A$, which
is independent of the superlattice size. Similar to the definition of

@@

It is also worth mentioning that the dielectric properties of 2D
materials are also often modeled using an effective medium approach,
which treats the 2D material as a slab with effective permittivity
$\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
\cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
methods require \textit{a priori} determination of $\delta$, a
quantity with controversial definitions \cite{Mas_Ballest__2011}. In
such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
determined by fitting the $L$-dependent data of
$\varepsilon_{\mathrm{SL}}$, which is not only computational
expensive, but also fails to capture the anisotropy of the 2D
dielectric properties (see Supplementary Section S1). On the
other hand, calculating 2D polarizabilities requires no knowledge of
$\delta$ (see Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
the polarizability as the true descriptor of 2D dielectric properties,
we will reveal the universal Moss-like relation of 2D materials.

@@

We study several types of 2D materials of different electronic and
optical properties as show in Figure \ref{fig-2}, including transition
metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
2D polarizabilities are calculated from the static dielectric response
of the selected 2D materials using density functional theory (DFT)
with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details).

Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
(blue dots) and polarizabilities (bar plots) of all the 2D materials
investigated, covering a wide spectrum range from far infrared to
ultraviolet. From dimension analysis, it is more intuitive to express
the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which has unit
of \AA. We find that $\alpha^{\parallel}$ has a general descending
trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (see
Supplementary Section S2.2).  Combining recent theoretical findings of
the universal linear relation between exciton binding energy
$E_{\mathrm{b}}$ and bandgap $E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to guess that
a general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha^{\parallel}$ may exist for 2D materials. On the other hand,
the bandgap-independent relation of $\alpha^{\perp}$ resembles
molecular polarizabilities of conjugate molecules \cite{Davies_1952},
fullerenes \cite{Sabirov_2014} and carbon nanotubes
\cite{Benedict_1995}, which are shown to be geometry-dependent. Next
we show that the universal Moss-like relations exist for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$.

@@

xy-plane. According to the random phase approximation (RPA)

@@

  = \lim_{\mathbf{q} \to 0} 1 + \frac{2e^{2}}{\varepsilon_{0} |\mathbf{q}|^{2} \Omega}
